hatchR: A toolset to predict hatch and emergence phenology in wild fishes

### 2025-03-06 inst/manuscript/paper.Rmd
WIP

```{r, fig.cap= "Effective value model fit and application for European Grayling. Panel A shows developmental rates (days to hatch) at five differrent average rearing temperatures and the corresponding model fit (blue line). Panel B uses the effective value model derived from the blue line in panel A to predict the effective value of daily average temperatures ranging from 2 to 14 °C. The dashed line is a 0.01 increase in effective value for every 1 °C increase as a point of reference.",fig.height= 8, fig.width=4,  fig.align = 'center', echo =FALSE}

grayling <- matrix(NA, 5, 2) |> tibble::tibble()
colnames(grayling) <- c("temp", "days")

grayling$temp <- c(2,5,8,11,14)
grayling$days <- c(106,51,29,19,13)

grayling_mod <- hatchR::fit_model(temp = grayling$temp,
                                  days = grayling$days,
                                  species = "grayling",
                                  development_type = "hatch")

@@

ef_vals <- NULL
for (x in temps){
  ef <- eval(parse(text = grayling_mod$expression$ expression))
  ef_vals <- rbind(ef_vals, ef)
}

grayling_ef <- matrix(NA, 13, 2) |> tibble::tibble()
colnames(grayling_ef) <- c("temp", "ef")
grayling_ef$temp <- temps
grayling_ef$ef <- ef_vals[,1]

@@

data_1 <- tibble(t = c(0:14), e = seq(0, 0.14, by =0.01))

p2 <- grayling_ef |>
  ggplot() +
  geom_point(aes(x = temp, y = ef)) +
  geom_line(aes(x = temp, y = ef)) +
  geom_line(data = data_1, aes(x = t, y = e), linetype = "dashed") +
  #geom_abline(intercept = 0, slope = .01, linetype = "dashed") +
  labs(x = "Daily average temperature (°C)", y = "Effective value") +
  theme_classic()

p1/p2 + plot_annotation(tag_levels = 'A')

```

>>>>

```{r, echo = FALSE, fig.height = 8, fig.width = 4,  fig.align = 'center', fig.cap = "Effective value model fit and application for European Grayling. Panel A shows developmental rates (days to hatch) at five differrent average rearing temperatures and the corresponding model fit (blue line). Panel B uses the effective value model derived from the blue line in panel A to predict the effective value of daily average temperatures ranging from 2 to 14 °C. The dashed line is a 0.01 increase in effective value for every 1 °C increase as a point of reference."}
grayling <- matrix(NA, 5, 2) |> tibble::tibble()
colnames(grayling) <- c("temp", "days")

grayling$temp <- c(2, 5, 8, 11, 14)
grayling$days <- c(106, 51, 29, 19, 13)

grayling_mod <- hatchR::fit_model(
  temp = grayling$temp,
  days = grayling$days,
  species = "grayling",
  development_type = "hatch"
)

@@

ef_vals <- NULL
for (x in temps) {
  ef <- eval(parse(text = grayling_mod$expression$ expression))
  ef_vals <- rbind(ef_vals, ef)
}

grayling_ef <- matrix(NA, 13, 2) |> tibble::tibble()
colnames(grayling_ef) <- c("temp", "ef")
grayling_ef$temp <- temps
grayling_ef$ef <- ef_vals[, 1]

@@

data_1 <- tibble(t = c(0:14), e = seq(0, 0.14, by = 0.01))

p2 <- grayling_ef |>
  ggplot() +
  geom_point(aes(x = temp, y = ef)) +
  geom_line(aes(x = temp, y = ef)) +
  geom_line(data = data_1, aes(x = t, y = e), linetype = "dashed") +
  # geom_abline(intercept = 0, slope = .01, linetype = "dashed") +
  labs(x = "Daily average temperature (°C)", y = "Effective value") +
  theme_classic()

p1 / p2 + plot_annotation(tag_levels = "A")
```
